```{r data generation, echo = FALSE, results = "hide"}
## regression parameters
n <- sample(40:90, 1)
b <- sample(c(-1, 1), 1) * runif(1, 1, 2) * sample(c(0.1, 0.5, 1), 1)
s <- sample(c(0.5, 1, 2), 1)

## data and regression
d <- data.frame(
  x = rnorm(n),
  err = rnorm(n, sd = s)
)
d$y <- 0 + b * d$x + d$err

## different types
type <- sample(c("linear", "semi-logarithmic", "log-log"), 1)
if(type == "linear") {
  m <- lm(y ~ x, data = d)
  xunit <- "unit" 
  yunit <- "units"
  eff <- round(coef(m)[2], digits = 2)
} else if(type == "semi-logarithmic") {
  d$y <- exp(d$y)
  m <- lm(log(y) ~ x, data = d)
  xunit <- "unit" 
  yunit <- "percent"
  eff <- round(100 * exp(coef(m)[2]) - 100, digits = 2)
} else if(type == "log-log") {
  d$y <- exp(d$y)
  d$x <- exp(d$x)
  m <- lm(log(y) ~ log(x), data = d)
  xunit <- "percent" 
  yunit <- "percent"
  eff <- round(100 * exp(0.01 * coef(m)[2]) - 100, digits = 2)
}

## summaries
direct <- if(coef(m)[2] > 0) "increases" else "decreases"
if(summary(m)$coefficients[2, 4] < 0.05) {
  sign1 <- "Also"
  sign2 <- ""
} else {
  sign1 <- "However"
  sign2 <- "_not_"
}
```

Question
========
Consider the following regression results:

```{r lm output, echo = FALSE, comment = NA}
summary(m)
```

Describe how the response `y` depends on the regressor `x`.


Solution
========
The presented results describe a `r type` regression.

The mean of the response `y` `r direct` with increasing `x`.

If `x` increases by 1 `r xunit` then a change of `y` by about `r eff` `r yunit` can be expected.

`r sign1`, the effect of `x` is `r sign2` significant at the 5 percent level.


Meta-information
================
extype: string
exsolution: nil
exname: regression essay
exextra[essay,logical]: TRUE
exextra[essay_format,character]: editor
exextra[essay_required,logical]: FALSE
exextra[essay_fieldlines,numeric]: 5
exextra[essay_attachments,numeric]: 1
exextra[essay_attachmentsrequired,logical]: FALSE
